### 2014-06-30 pot/LaTeX/skewnormal.tex
Found some mistakes in the MCMC
Made an adjustment so all calculations account for the fact that the z
term already incorporate sigma when it's generated. Also general
adjustments to incorporate misc bugs in the code.
Updates to simplify the mcmc

\subsection{Complete data}\label{s:model}
Consider the spatial process
\begin{align} \label{eq:fullmodel}
  Y_t(\bs) &= X_t(\bs) \beta + e_t(\bs)\\
  e_t(\bs) &= \delta z_t(\bs) + v_t(\bs)
\end{align}
where $z_t(\bs) = z_{tl}$ if $s \in P_{tl}$ where $P_{t1}, \ldots, P_{tL}$ form a partition, and $z_{tl} \iid N_{(0, \infty)}(0, \sigma_t^2)$, $\delta \in (-1, 1)$ controls skew, and $v_t(\bs)$ is a spatial Gaussian process with mean zero and variance $\sigma_t^2(1 - \delta^2)$.

Then $Y_t(\bs)$ is skew normal within each partition \citep{Minozzo2012}.
We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tL}$ be partition centers so that
\begin{align*}
  P_{tl} = \{\bs_t : l = \argmin_k || \bs_t - w_{tk} ||\}.
\end{align*}
Then
\begin{align}
    Y_t(\bs) \mid \Theta, z_{t1}, \ldots, z_{tL} &= X_t(\bs) \beta + \delta z_t(\bs) + v_t(\bs) \label{eq:hier}\\
    z_{tl}(\bs) \mid \Theta &\sim N_{(0, \infty)}(0, \sigma^2_t)\\
    v_t(\bs) \mid \Theta &\sim \Matern(0, \Sigma)\\
    \sigma &\sim IG(\alpha, \beta)\\
    \delta &\sim Unif(-1, 1)\\
    w_{tk} &\sim Unif(\calD)
\end{align}
where $\Theta = \{w_{t1}, \ldots, w_{tL}, \beta, \sigma_t, \delta, \rho, \nu \}$; $l = \argmin_k ||\bs - w_k ||$; $\Sigma_t$ is a \Matern covariance matrix with variance $\sigma_t^2 (1 - \delta^2)$, spatial range $\rho$ and smoothness $\nu$; and $\calD$ is the spatial domain of interest.

@@

\subsection{Parameter updates}\label{s:params}
To update $\Theta$ given the current value of the complete data $\bY_1, \ldots, \bY_T$, we use a standard Gibbs updates for all parameters except for the knot locations which are done using a Metropolis update.
See Appendix A.1 for details regarding Gibbs sampling and $|u_t(\bs)|$.

@@

\section*{Appendix A.1: Posterior distributions}
\input{zpost.tex}
\input{betapost.tex}
\input{sigpost.tex}

>>>>

\subsection{Complete data}\label{s:model}
Consider a skew Gaussian spatial process
\begin{align} \label{eq:fullmodel}
  Y_t(\bs) &= X_t(\bs) \beta + \sigma_1 z_t(\bs) + v_t(\bs)
\end{align}
where $z_t(\bs) = z_{tl}$ if $s \in P_{tl}$ where $P_{t1}, \ldots, P_{tL}$ form a partition, and $z_{tl} \iid N_{(0, \infty)}(0, 1)$, $\sigma_1 \in \calR$, $\sigma_2, \sigma_0 \in \calR^+$, and $v_t(\bs)$ is a spatial Gaussian process with mean zero and variance $\sigma_{tl}^2$.
It can be shown \citep{Zhang2010} that $Y_t(\bs)$ follows a skew normal distribution with skewness parameter $\alpha = \frac{ \sigma_1 }{ \sigma_{tl} }$.
We can then reexpress the model in (\ref{eq:fullmodel}) as
\begin{align}
  Y_t(\bs) &= X_t(\bs) \beta + \alpha z_t(\bs) + v_t(\bs)
\end{align}
where $z_t(\bs) = z_{tl}$, $z_{tl} \iid N_{(0, \infty)}(0, \sigma_{tl}^2)$, and $v_t(\bs)$ is defined as before.

We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tL}$ be partition centers so that
\begin{align*}
  P_{tl} = \{\bs_t : l = \argmin_k || \bs_t - w_{tk} ||\}.
\end{align*}
Then
\begin{align}
    Y_t(\bs) \mid \Theta, z_{t1}, \ldots, z_{tL} &= X_t(\bs) \beta + \alpha z_t(\bs) + v_t(\bs) \label{eq:hier}\\
    z_{tl}(\bs) \mid \Theta &\sim N_{(0, \infty)}(0, \sigma^2_{tl})\\
    v_t(\bs) \mid \Theta &\sim \Matern(0, \Sigma)\\
    \sigma^2_{tl} &\iid IG(\alpha, \beta)\\
    \alpha &\sim N(0, 10)\\
    w_{tk} &\sim Unif(\calD)
\end{align}
where $\Theta = \{w_{t1}, \ldots, w_{tL}, \beta, \sigma_t, \delta, \rho, \nu \}$; $l = \argmin_k ||\bs - w_k ||$; $\Sigma_t$ is a \Matern covariance matrix with variance $\sigma_{tl}^2 (1 - \delta^2)$, spatial range $\rho$ and smoothness $\nu$; and $\calD$ is the spatial domain of interest.

@@

\subsection{Parameter updates}\label{s:params}
To update $\Theta$ given the current value of the complete data $\bY_1, \ldots, \bY_T$, we use a standard Gibbs updates for all parameters except for the knot locations which are done using a Metropolis update.
See Appendix A.1 for details regarding Gibbs sampling.

@@

\section*{Appendix A.1: Posterior distributions}
\input{zpost.tex}
\input{betapost.tex}
\input{sigpost.tex}
\input{alphapost.tex}
